Put Title here

### 2018-12-12 General WLD combinatorics.tex
minor typo fix

\begin{lem}\label{lem basis as perm}
Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and let $M(W)$ be its associated matroid. A subset $J \subseteq [n]$ is an independent set of $M(W)$ if and only if there exists an injective set map $f : J \rightarrow \cP$ with the property that for each $s\in S$ we have $s \in V(f(s))$.
\end{lem}

>>>>

\begin{lem}\label{lem basis as perm}
Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and let $M(W)$ be its associated matroid. A subset $J \subseteq [n]$ is an independent set of $M(W)$ if and only if there exists an injective set map $f : J \rightarrow \cP$ with the property that for each $j\in J$ we have $j \in V(f(j))$.
\end{lem}
